Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-13 manuscript/manuscript.tex
Update linear density figure caption

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/linear-density-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by each tesseroid shell model
    and the analytical solution.
    Each model has a linear density function of radius (Eq. \ref{eq:density-linear}).
    The computations were performed on the four combinations described in
    Table \ref{tab:grids}.
    Each line represents the maximum absolute difference between every shell model with
    a certain thickness.
    Due to the linearity of the density function, the density-based discretization
    algorithm is not applied.
    Differences are reported as a percentage of the shell values.
    The horizontal dashed black line represents a target difference of 0.1\%.
}
\label{fig:D-linear}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/linear-density-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by each tesseroid shell model
    and the analytical solution.
    Each model has a linear density function (Eq. \ref{eq:density-linear}).
    The computations were performed on the four grids described in
    Table~\ref{tab:grids} and using 20 shell models built with the tesseroids
    collections detailed in Table~\ref{tab:tess-collections} and five different
    thicknesses.
    Each line represents the maximum absolute difference between every shell model with
    a certain thickness.
    Due to the linearity of the density function, the density-based discretization
    algorithm is not applied.
    Differences are reported as a percentage of the shell values.
    The horizontal dashed black line represents a target difference of 0.1\%.
}
\label{fig:D-linear}
\end{figure*}
